Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-05-06 response.tex

\response{We did a 2-fold cross validation by using 20\% of the data for testing and the remainder for training within each scene. We learned separate collections of vector fields and model parameters for each fold on all of the four scenes on which we tested.}

\begin{item}
\textbf{The motivation behind choosing the affinity propagation clustering
algorithm is not clearly stated. 
What is the distance measure used (i.e Euclidian, \"{O}) ? Not specifying
such information makes reproduction of this work not feasible. }

This was an oversight on our part, thank you for noticing it. The distance used is actually a custom distance function on $\mathbb{R}^4$, which disregards the involution $(x_1, x_2, x_3, x_4) \to (x_3, x_4, x_1, x_2)$, and so doesn't care about parity of trajectories. We have included the following clarification:

\response{We then cluster in $\mathbb{R}^4$ using Affinity Propagation[17] and a custom distance measure defined by $d((x_1, x_2, x_3, x_4),\mathbf{y}) : \mathbb{R}^4 \times \mathbb{R}^4 \to \mathbb{R} = \min \left\{ d_e((x_1, x_2, x_3, x_4), \mathbf{y}), d_e((x_3, x_4, x_1, x_2), \mathbf{y}) \right\}$, for the euclidean distance $d_e$. This function measures the distance between the endpoints irrespective of their ordering. The scale of the datasets we tested on had large enough spatial scale that clustering based on endpoints captured people moving from destination to destination, e.g. from a storefront to the sidewalk at the edge of a scene. On our data, other distance measures from \todo{[Morris and Trivedi]} and \todo{[Lee 2007]} didn't identify coherent motion models. This is partly due to the fact that oftentimes pedestrians would take slightly different routes to get to their destination, but the cumulative effect on the distance measures is enough to hinder the clustering. }

@@

\end{item}

\begin{item}
\textbf{Adequacy of Citation
I believe literature review section can be improved using a sub section
on social force models, which is extensively applied for pedestrian
trajectory forecasting. 
Helbing and Molnar, 1995; Koppula and Saxena, 2013; Pellegrini et al.,
2010; Yamaguchi et al., 2011; Xu et al., 2012; Wang et al. 2008;
Hospedales et al. 2009; Emonet et al. 2011; Yi et al. 2015.}
\end{item}

We agree that this adds to the paper, thank you for the suggestion. We added a section to our literature to reflect the relevant work.

	\response{On the other hand, authors have approached pedestrian forecasting by deriving their motion model from interactions between pedestrians. Early work by [helbig] and [Xu] describe pedestrians interactions using physically motivated tools. Several models [yamaguchi, yi, pellegrini you’ll never] derive their motion models from [helbing] which incorporates collision avoidance through an interaction potential which repels pedestrians from each other, leading to forms of Linear Trajectory Avoidance (LTA). However LTA suffers from not planning for other pedestrian’s positions at future times. [emonet], [hospedales], and [wang: unsupervised] all take optical flow as input. [wang] and [emonet] both use variants of Hierarchical Dirichlet Processes on discretized optical flow to determine temporal motifs (i.e. classes of motion within the scene), where [hospedales] substitutes a Markov model. These models are not agent based, and the lack of an explicit motion model limits their predictive power in situations where we know more about the data. [koppula and saxena] predict trajectories by introducing and sampling Anticipatory Temporal Conditional Random Fields which incorporate human affordances relating to human objectives within the scene. [Tay], [Wang jw], and [Trautman] create agent-based models based on Gaussian Processes, though they suffer issues when trained on discretized trajectories. [alahi] uses Long Short-Term Memory to learn pedestrian motion models without making implicit (as in the case of CRFs) or explicit (in the case of social forces) assumptions about the manner in which agents will interact. [alahi] outperformed LTA, and social forcing based on [yamaguchi]  and IGP from [trautman]. Along with its quick run time, this motivated our decision to test our algorithm against it.  }

\begin{item}
\textbf{Furthermore a comprehensive review on trajectory clustering algorithms
is required. This should be used to motivate the reason of choosing
affinity propagation algorithm in section 4. 
Morris and Trivedi 2009; Giannotti et al. 2007; Lee et al. 2007;
Ester et al. 1996 }

### 2017-05-06 paper/pedestrian_forecasting_iros_2017.tex
Add lit review

>>>>

\rtext{On the other hand, authors have approached pedestrian forecasting by deriving their motion model from interactions between pedestrians. Early work by [helbig] and [Xu] describe pedestrians interactions using physically motivated tools. Several models [yamaguchi, yi, pellegrini you’ll never] derive their motion models from [helbing] which incorporates collision avoidance through an interaction potential which repels pedestrians from each other, leading to forms of Linear Trajectory Avoidance (LTA). However LTA suffers from not planning for other pedestrian’s positions at future times. [emonet], [hospedales], and [wang: unsupervised] all take optical flow as input. [wang] and [emonet] both use variants of Hierarchical Dirichlet Processes on discretized optical flow to determine temporal motifs (i.e. classes of motion within the scene), where [hospedales] substitutes a Markov model. These models are not agent based, and the lack of an explicit motion model limits their predictive power in situations where we know more about the data. [koppula and saxena] predict trajectories by introducing and sampling Anticipatory Temporal Conditional Random Fields which incorporate human affordances relating to human objectives within the scene. [Tay], [Wang jw], and [Trautman] create agent-based models based on Gaussian Processes, though they suffer issues when trained on discretized trajectories. [alahi] uses Long Short-Term Memory to learn pedestrian motion models without making implicit (as in the case of CRFs) or explicit (in the case of social forces) assumptions about the manner in which agents will interact. [alahi] outperformed LTA, and social forcing based on [yamaguchi]  and IGP from [trautman]. Along with its quick run time, this motivated our decision to test our algorithm against it. }
